%-------------------------
% Resume in Latex
% Author : Frederick Go
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tabto}
\input{glyphtounicode}

% Font
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large 
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% New bullet point style
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$ \hspace{0pt}}
\newcommand{\resumeGroupListStart}{\begin{itemize}[leftmargin=0.05in, label={}]}
\newcommand{\resumeGroupListEnd}{\end{itemize}}
\newcommand{\resumeSingleLineHeading}[2]{
    \item
        \begin{tabular*}{0.985\textwidth}{l@{\extracolsep{\fill}}r}
          #1 & \small#2 \\
        \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeDoubleLineHeading}[4]{
    \vspace{-2pt}\item
        \begin{tabular*}{0.985\textwidth}[t]{l@{\extracolsep{\fill}}r}
            #1 & \small#2 \\
            \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\resumeItem}[1] {\item\small {#1 \vspace{-4pt}}}

%---------------------------------RESUME STARTS HERE---------------------------------
\begin{document}
%---------------------------------HEADING---------------------------------
\begin{center}
    \textbf{\Huge \scshape Frederick Go} \\ \vspace{1pt}
    \href{mailto:hyeongo0317@gmail.com}{\underline{hyeongo0317@gmail.com}} $|$ 
    \small 902-580-3648 $|$ 
    \href{https://linkedin.com/in/fred-go}{\underline{linkedin.com/in/fred-go}} $|$
    \href{https://github.com/itsmefredgo}{\underline{github.com/itsmefredgo}} $|$
    \href{https://freddiego.dev}{\underline{freddiego.dev}}
\end{center}
%---------------------------------EXPERIENCE---------------------------------
\section{Experience}
    \resumeGroupListStart
  
        \resumeDoubleLineHeading
            {\textbf{Machine Learning Operations Engineer Intern - Production Pipeline Team Lead}}{May 2024 - Aug 2024}
            {VosynAI}{Toronto, ON (remote)}
        \resumeItemListStart
            \resumeItem{Led a team of 18 engineers in designing and building a robust pipeline for a global CDN service, aiming to support 200+ million users.}
            \resumeItem{Orchestrated agile sprints, effectively managing task assignments and team progress through weekly meetings.}
            \resumeItem{Automated Docker image build and deployment using GitHub Actions/Workflow, integrating with AWS services}
            \resumeItem{Architected and provisioned scalable AWS infrastructure, including Lambda, EC2, ECR, ECS, and S3, to support the pipeline's development and maintenance.}
            \resumeItem{Served as the primary point of contact for cross-functional collaboration between different teams and departments.}
            \resumeItem{Developed Python scripts for efficient processing of multi-modal data, enhancing the user experience by optimizing performance and reducing latency.}
        \resumeItemListEnd
    
        \resumeDoubleLineHeading
            {\textbf{Full-stack Developer} \emph{\small{(freelance/volunteer)}}}{Dec 2022 - Present}
            {St. Joseph’s Children’s Centre}{Halifax, NS (On-call/hybrid)}
        \resumeItemListStart
            \resumeItem{Revitalized and updated the organization's website, on WordPress \& PHP, to ensure accurate and current information.}
            \resumeItem{Addressed prior site neglect, resolving issues promptly and ensuring the site now provides up-to-date information.}
            \resumeItem{Resolved issues with email inquiries resulting in clients in interest sending emails via a form easily.}
        \resumeItemListEnd

        \resumeDoubleLineHeading
            {\textbf{Web Developer} \emph{\small{(freelance)}}{\small[\href{https://www.parkbomacademy.com}{\underline{Visit}}]}}{Jan 2024 - Mar 2024}
            {Parkbom Academic Institution}{Geoje, South Korea (remote)}
        \resumeItemListStart
            \resumeItem{Led the development and launch of a responsive website using NextJS ensuring 99.99\% uptime via AWS.}
            \resumeItem{Developed a website leading to 20\%+ increase in incoming inquiries with many questions answered prior to appointments.}
            \resumeItem{Collaborated with cross-functional stakeholders to gather feedback including modifying based on business requirements.}
        \resumeItemListEnd

  \resumeGroupListEnd
%---------------------------------EDUCATION---------------------------------
\section{Education}
    \resumeGroupListStart
    
        \resumeDoubleLineHeading
            {\textbf{Dalhousie University}}{Sep 2020 -- May 2023}
            {Bachelor of Computer Science, Minor in Statistics (GPA: 4.15 / 4.3)}{Halifax, NS}
        \resumeItemListStart
            \resumeItem{Certifications: Communication Technologies \& Cyber Security, Data Science}
        \resumeItemListEnd
        
    \resumeGroupListEnd

%---------------------------------PROJECTS---------------------------------
\section{Projects}
    \resumeGroupListStart
    
        \resumeSingleLineHeading
            {\textbf{freddiego.dev} $|$ \emph{NextJS, Sanity.io, TailwindCSS, TypeScript, Vercel, etc.}{\small[\href{https://freddiego.dev}{\underline{Visit}}]}}{Mar 2024 - Present}
        \resumeItemListStart
            \resumeItem{Personal portfolio website showcasing expertise with responsive design, constantly evolving with new features where I test and learn the newest and the latest technologies.}
        \resumeItemListEnd
          
        \resumeSingleLineHeading
            {\textbf{NotifyAll} $|$ \emph{AWS (EC2, DynamoDB, Lambda...), NextJS, Python, Docker, Vercel, etc.}{\small[\href{https://www.youtube.com/watch?v=HWyE7KBI-ww}{\underline{Demo}}]}}{Jan 2023 - Apr 2022}
        \resumeItemListStart
            \resumeItem{Developed a SaaS web service with AWS backend and NextJS frontend, aimed to learn Cloud Computing in depth. }
        \resumeItemListEnd

        \resumeSingleLineHeading
            {\textbf{Trello Platform Clone } $|$ \emph{Java, JUnit, JavaScript, React, Material UI, MySQL, etc.}}{May 2022 - Aug 2022}
        \resumeItemListStart
            \resumeItem{Cloned and built a meeting management platform, Trello, following agile principles.}  
        \resumeItemListEnd

        \resumeSingleLineHeading
            {\textbf{Mini Blogs} $|$ \emph{PHP, MySQL, etc.}{\small[\href{https://web.cs.dal.ca/~dgo/}{\underline{View}}]}}{Sep 2021 - Nov 2021}
        \resumeItemListStart
            \resumeItem{Developed a mini blog website with a focus on server-side scripting and frontend-backend integration.}
        \resumeItemListEnd

    \resumeGroupListEnd
%---------------------------------PROGRAMMING SKILLS---------------------------------
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
            \textbf{Languages}{: Java, Python, C/C\#, MySQL, JavaScript, TypeScript, HTML/CSS, PHP, R} \\
            \textbf{Frameworks}{: Next.js, React, TailwindCSS, JUnit, Material UI, Bootstrap} \\
            \textbf{Tools/Libraries}{: Pandas, NumPy, Matplotlib, ScikitLearn, Git, Docker, AWS, VSCode, Wireshark, MongoDB, DynamoDB} \\
            \textbf{Others}{: Vercel, Node.js, Scrum, Agile, RestAPI, IDEs (VSCode, IntelliJ), Figma, Microsoft Office, Slack}
        }}
    \end{itemize}
    \vspace{-15pt}
%---------------------------------Leadership---------------------------------
\section{Leadership Experience}
    \resumeGroupListStart
        \resumeSingleLineHeading
            {\textbf{Course Representative} - Dalhousie University}{}
        \resumeItemListStart
            \resumeItem{Served as a course representative to represent the classes, developing strong leadership, and communication skills.}
            % \resumeItem{Organized feedback, and resolved raised concerns within the classes. Developed strong leadership, and communication skills.}
        \resumeItemListEnd
        
    \resumeGroupListEnd
    % \vspace{-10pt}
%---------------------------------Certifications---------------------------------
\section{Certifications \& Awards}
    \resumeGroupListStart
        \item 
        \vspace{3pt}
        \resumeItemListStart
            \resumeItem{Google Data Analytics Certificate}
            \resumeItem{Docker Foundations Professional Certificate}
            \resumeItem{Sexton Scholar/Distinctions (Dalhousie University): Awarded to those who maintain 3.85+ GPA}
        \resumeItemListEnd
    \resumeGroupListEnd
%---------------------------------
\end{document}
